\section{Experimental Design}
\label{sec:evaluation}

\subsection{Study Setup}

We ran a between-subjects experiment with two conditions. In the first, participants attended a spoken lesson delivered by the AI teacher while an AI peer student was also present. In the second, participants attended the same lesson with the teacher only. Both conditions covered the same topic: Simpson's Paradox. Participants were recruited informally among students at Heriot-Watt University, and each session lasted roughly 10 to 15 minutes. We collected 19 complete responses in total: 9 in the Teacher and AI peer group, and 10 in the Teacher only group.

\subsection{Questionnaire Design}

After their session, participants filled in a questionnaire with four parts. The first asked them to rate their prior familiarity with Simpson's Paradox on a 1 to 5 scale. The second collected Likert ratings on content clarity, engagement, pace, and post-session confidence. Participants in the Teacher and AI peer group also rated the peer student directly on helpfulness and classroom feel. The third part contained seven knowledge questions, ranging from basic recall to applied reasoning, plus two visual questions. The fourth part gathered open-ended qualitative feedback.

\subsection{Analysis}

We report group means and run independent-samples t-tests to compare the two conditions. Given the small sample sizes, no result should be treated as conclusive, and the t-tests are included primarily for completeness.


\section{Results}
\label{sec:results}

\subsection{Prior Knowledge}

Both groups started from a similar baseline: mean prior familiarity of 1.78 for the Teacher and AI peer group and 1.60 for the Teacher only group, confirming that most participants had little to no prior knowledge of Simpson's Paradox.

\subsection{Learning Experience}

Table~\ref{tab:experience} shows mean ratings and t-test results for both groups across the four learning experience items.

\begin{table}[H]
\centering
\footnotesize
\setlength{\tabcolsep}{4pt}
\begin{tabular}{lcccc}
\toprule
\textbf{Item} & \textbf{T+AI} & \textbf{T-only} & \textbf{t} & \textbf{p} \\
\midrule
Content clarity    & 4.22 & 4.00 & 0.506 & 0.620 \\
Engagement         & 4.00 & 3.50 & 1.269 & 0.222 \\
Pace               & 4.33 & 4.10 & 0.702 & 0.492 \\
Post-conf.\        & 4.67 & 4.30 & 0.946 & 0.357 \\
\bottomrule
\end{tabular}
\caption{Mean learning experience ratings by condition (1--5 scale; T+AI $n=9$, T-only $n=10$).}
\label{tab:experience}
\end{table}

The Teacher and AI peer group rated their experience slightly higher across all four dimensions, with the largest gap in engagement (4.00 versus 3.50) and post-session confidence (4.67 versus 4.30). None of the differences reached statistical significance. Participants in the Teacher and AI peer group rated the peer student's helpfulness at 4.33 on average, and its contribution to classroom feel at 5.00, suggesting they found its presence genuinely useful even where the scores did not diverge significantly from the other group.

\subsection{Knowledge Assessment}

Table~\ref{tab:knowledge} reports correct answer counts per question and overall mean scores.

\begin{table}[H]
\centering
\footnotesize
\setlength{\tabcolsep}{4pt}
\begin{tabular}{lcc}
\toprule
\textbf{Question} & \textbf{T+AI} & \textbf{T-only} \\
\midrule
Q9  Definition              & 8/9  & 7/10 \\
Q10 Berkeley example        & 9/9  & 9/10 \\
Q11 Confounding variables   & 7/9  & 7/10 \\
Q12 Common misconception    & 5/9  & 4/10 \\
Q13 Critical context        & 7/9  & 7/10 \\
Q14 First step              & 8/9  & 9/10 \\
Q15 Applied scenario        & 3/9  & 5/10 \\
Q16 Visual identification   & 6/9  & 7/10 \\
Q17 Practical example       & 6/9  & 8/10 \\
\midrule
\textbf{Mean /9}            & \textbf{6.67} & \textbf{6.30} \\
\bottomrule
\end{tabular}
\caption{Knowledge assessment results by condition ($t=0.382$, $p=0.707$; T+AI $n=9$, T-only $n=10$).}
\label{tab:knowledge}
\end{table}

Overall knowledge scores were similar between the two groups (74.1\% versus 70.0\%), and the t-test found no significant difference (t = 0.382, p = 0.707). Both groups performed well on definitional questions and struggled with the applied scenario (Q15) and the practical example (Q17), where the Teacher only group actually scored slightly higher. Answer confidence followed the same pattern as post-session confidence, with the Teacher and AI peer group rating slightly higher (3.89 versus 3.30, p = 0.190).

\subsection{Qualitative Feedback}

Responses were broadly positive in both groups. The most consistent criticism was pacing: participants across both conditions found the speech too slow and mentioned that silences between turns broke immersion. Several also noted that the teacher jumped into technical content without a brief introduction, which made the opening harder to follow. In the Teacher and AI peer group, most participants either did not identify the peer as an AI during the session, or said it did not affect their experience when they did. A few noted the peer's questions were helpful. Recurring suggestions included faster TTS, a short contextual introduction before the lesson begins, and more interactive question slots for the human.

\subsection{Discussion}

The results do not show a clear advantage for either condition in terms of knowledge scores or experience ratings. Both groups reached a similar level of understanding, and no t-test approached significance. The most plausible explanation is that the lesson itself was effective enough to produce consistent results regardless of condition, and that several of the knowledge questions were too straightforward to discriminate between groups. The harder applied questions (Q15, Q17) are more informative in this regard, and the Teacher only group actually performed marginally better on those, though the difference is small and within noise.

Where the two conditions do differ more noticeably is in engagement and post-session confidence, with the Teacher and AI peer group rating both higher. This is consistent with what the vicarious learning hypothesis would predict: having a peer present may enrich the perceived experience even when objective test scores are equivalent. The peer student ratings (4.33 for helpfulness, 5.00 for classroom feel) support this reading.

The main limitations are the small and informally recruited sample, the ceiling effect on simpler knowledge questions, and one participant who already knew the system, which biases their responses. A larger, more controlled study with pre-screened participants and improved TTS pacing would be needed to draw firmer conclusions.
