\section{Implementation}
\label{sec:implementation}
% ============================================================
% MARKING CRITERION: "Implementation" [20 marks]
%   - Significant amount of work done in system implementation
%   - Resulting system functions well and is of appropriate complexity

\guidance{%
  MARKING: This section is worth 20 marks. The marker will assess:
  (1) whether a significant amount of implementation work has been done,
  and (2) whether the resulting system functions well and is of
  appropriate complexity. Focus on \emph{how} you built the system:
  technical details, libraries/APIs used, algorithms, data structures,
  challenges encountered and how you solved them. Include code snippets,
  pseudocode, or detailed descriptions where they help convey complexity
  and effort. If you compared alternative implementations, describe the
  comparison and rationale.}

\subsection{Component A --- Implementation Details}

\guidance{%
  Describe the implementation of this component. What libraries, models,
  or APIs did you use? What was non-trivial about making it work?}

% Write implementation details for component A.

\subsection{Component B --- Implementation Details}

\guidance{%
  Detail the implementation steps. For a dialogue manager, for example,
  describe the slot-filling loop, prompt engineering, error handling,
  state management, etc.}

% Example structure for a pipeline component:
% \textbf{Step 1 --- Slot Prompting:} ...
% \textbf{Step 2 --- Slot Filling:} ...
% \textbf{Step 3 --- User Input Handling:} ...
% \textbf{Step 4 --- Slot Value Updating:} ...
% \textbf{Step 5 --- Task Completion:} ...

\subsection{Component C --- Implementation Details}

% Write implementation details for component C.

\subsection{Integration and Challenges}

\guidance{%
  Describe how the components were integrated into a working system.
  Discuss any significant challenges encountered during development
  and how they were resolved. This demonstrates the depth of work done
  and helps justify the ``significant amount of work'' criterion.}

% Write integration and challenges here.
