\section{Previous Work}
\label{sec:previous_work}
% ============================================================
% MARKING CRITERION: "Literature Review" [40 marks]


\subsection{Dialogue, Vicarious Learning, and Educational Conversational Agents}
\label{sec:background}

For nearly two decades, spoken dialogue systems (SDS) have been
investigated in educational contexts, particularly for intelligent
tutoring \citep{litman2004itspoke, pon-barry2004scot} and language
learning \citep{seneff-etal-2007-spoken, bibauw2019dialogue}, and more
recently as conversational agents powered by large language models
\citep{Sydorenko2025}. Dialogue has been demonstrated to be a more effective modality than plain
text for knowledge retention \citep{ginns2013designing}, and merely
\emph{overhearing} dialogue between agents has itself been shown to
support learning better than listening to a monologue \citep{vicarious_learning}.

This phenomenon, coined vicarious learning, has been investigated
through "fictive dialogues": semi-scripted exchanges between virtual
agents generated from a source text, where the learner is a passive
listener rather than an active participant \citep{piwek2007t2d}.
\citet{fictive_dialogs} extend this concept to a classroom
language-learning Educational Conversational Agent (ECA) that
alternates between teacher and peer roles. They find that more
scripted agent and human-confederate exchanges improve comprehension, whereas
direct agent-to-learner questioning degrades it.
The multi-party configurations needed for designing unscripted agentic
conversations remain a known open challenge for current systems
\citep{aylett2023you, skantze2021turntaking}, primarily because
realtime end-of-turn prediction, speaker detection and interruption
handling all become critical in a non-deterministic dialogue. 

\subsection{LLM-based and Multi-Agent Tutors}
\label{sec:llm_tutors}

A recent systematic review of 36 educational chatbots finds that
teaching agents and peer agents together dominate role assignments
\citep{kuhail2023interacting}. This decomposition maps directly
onto the agentic teacher and question-asking student configuration the
present system adopts. However, empirical evidence on the pedagogical effects
of the LLM-based variants of such systems is only
beginning to accumulate. \citet{SpangenbergerPia2026CwaL}
evaluate chat-based conversation with an LLM in education for
sustainable development, and find that LLM chat engages both
affective and cognitive processes relevant to
learning, and results in knowledge gains comparable to reading the same
material as text. This establishes LLM chat as a viable teaching
medium, but does fall short in larger, structured tasks such as robust curricular sequencing and student modelling. 
This underpinned the learning gains reported for earlier conversational intelligent tutoring systems such as AutoTutor \citep{graesser2016autotutor}.

A recent architectural response to recover the teaching
structure, is by composing several specialised LLM agents rather than
relying on a single chatbot or a scripted dialogue policy. The
WikiHowAgent system of \citet{pei-etal-2025conversational}
implements teacher, student, interaction-manager and evaluator
agents at scale. \citet{shi-etal-2025-educationq} apply a similar teacher-student-evaluator 
framework (EducationQ) to benchmark teaching ability across 14 LLMs. Both systems, however, place no
human in the interactive loop, typically the human enters only as a
post-hoc judge. Our work attempts to close this gap using a human learner, 
embedded in realtime dialogue rather than generated text, that follows a similar student-teacher-evaluator role decompostion. 


\subsection{Speech Interfaces for Educational Agents}
\label{sec:speech_interfaces}

The few LLM-based ECAs that do operate in through speech
typically pair their dialogue manager with a cloud-based speech I/O pipeline.
\citet{fictive_dialogs}, for instance, integrate Deepgram's hosted
ASR and TTS synthesis into a RASA dialogue agent.
\citet{Sydorenko2025} identify recognition error and end-to-end
latency as the two persistent bottlenecks for spoken educational
agents. This is a concern espeacially relevant to realtime turn-taking
\citep{skantze2021turntaking}. The present system adopts the same
two-component STT/TTS split but runs both locally (using Whisper for STT,
and Chatterbox for TTS). By doing this, we trade on-device compute for lower latency
and no external dependency in the realtime loop, which addresses the key issues \citep{Sydorenko2025} for fluent spoken interaction.

\subsection{Summary}
\label{sec:prev_work_summary}

Our system sits at the intersection of three research fields: the
dialogue-based intelligent tutoring field
\citep{litman2004itspoke, pon-barry2004scot} with its spoken,
pedagogically-structured interaction. The recent LLM-based tutor
research \citep{SpangenbergerPia2026CwaL, pei-etal-2025conversational},
which contributes fluent generation and scalable multi-agent role
decomposition but operates in text-only, typically restricted to one-to-one agent dialogues or monologues. 
Lastly, the vicarious dialogue paradigm
\citep{vicarious_learning, piwek2007t2d, fictive_dialogs}, which shows
that overhearing pedagogically structured dialogue between agents
improves learning. The system's central design move is to substitute
the scripted human confederate of \citet{fictive_dialogs} with a
second autonomous LLM agent. This serves as a novel combination of the teacher-learner agent
decomposition of \citet{pei-etal-2025conversational} with the
overhearing-learner stance of the fictive-dialogue tradition, over a
realtime spoken channel. Closing this gap opens the door to emerging
application areas such as spoken classroom assistants, 
accessibility-focused tutors for low-literacy learners, multi-party
language-learning environments, and healthcare communication training.
