\section{System Design and Architecture}
\label{sec:design}

To implement the proposed multy-party dialog project, we designed and orchestrated a system with multiple different technologies. This section, gives an overview on the system design and technologies used.

\subsection{Architecture Overview}

As it can be seen in \autoref{fig:architecture}, the project is divided into 3 programs which work strategically together; Turn-taking Controller (TTC), Teacher and Student. The communication between the programs is based in a TCP socket connection where the TTC acts as the server and the Teacher and Student function as clients. The information which is transmitted through the sockets are serialized json objects containing events information, in \autoref{lst:json-event-example} an example of serialized JSON event can be seen.


\begin{lstlisting}[
  language=json,
  caption={JSON agent\_text\_chunk event example},
  captionpos=b,
  label={lst:json-event-example},
]
{
    "type": "agent_text_chunk",
    "role": 2,
    "text": "Today's topic is the Spanish Empire.",
    "ts": 1713187200000
}
\end{lstlisting}

\subsubsection{TTC}
The TTC acts a the TCP server where the teacher and student establish connections to it. Furthermore, the TTC has 2 main roles. First, managing all the events happening in the system and taking decisions based on the status of the system. Second, handling all the information extracted from and trasmitted to the human. It is composed by 3 internal components:


\textbf{ASR.} It detects the user speech and streams the transcription of what the user said. When silence is detected the component emits an \texttt{end\_of\_utterance} event.

\textbf{TTS.} Works with streams of text, playing as audio what either agent generated.

\textbf{Event Handlers.} The main orchestrator of the whoel system. It received events from both agents, and from the \textbf{ASR} and \textbf{TTS}, based on that it manages all the system by selecting the next speaker or waiting for the human to talk if needed. based on that it manages all the system by selecting the next speaker or waiting for the human to talk if needed.

\subsubsection{Teacher}
The Teacher is a client program that connects to the TTC. It loads an initial lesson script and uses an LLM with a teaching-focused system prompt to generate responses to both students.

\subsubsection{Student}
The Student is a client program that connects to the TTC. It maintains conversation state and generates clarifying questions using an LLM focusing on improving tha human comprehension and knoweledge.

\subsection{Workflow}


This section will give an overview of the workflow of the system for both experiments: with peer student and without it.

% TODO: Mention all the possible events that can be sent through the sockets

\subsubsection{With peer student}
\autoref{fig:seq_combined} shows the sequence diagram of the system. First, once both clients are connected to the TTC, the latter sends the \texttt{agent\_turn} to the Teacher which starts streaming a pre-generated initial lesson. Once the Teacher has finished streaming the lesson to the TTC, it emits a \texttt{agent\_text\_end} event signaling that it has finished streaming text. Afterwards, the TTC performs two actions in parallel; First, it starts bounces the \texttt{agent\_text\_end} event to the Student so the student can start generating its own possible intervention. While

\subsubsection{Without peer student}

\autoref{fig:seq_combined} shows a sequence diagram of the teacher-student worfkflow.


\begin{table*}[htbp]
\small
\centering
\begin{tabular}{llll}
\toprule
\textbf{Event} & \textbf{Sender} & \textbf{Receiver} & \textbf{Description} \\ \midrule
\texttt{human\_transcription} & All Clients & TTC & Human speech transcription \\
\texttt{agent\_text\_chunk} & TTC & All clients & Text chunk from agent stream \\
\texttt{agent\_text\_end} & TTC & All clients & End of agent response \\
\texttt{agent\_turn} & TTC & Client & Signal for agent to start turn \\
\texttt{agent\_turn\_cancelled} & TTC & Client & Turn cancelled (interrupted) \\ \bottomrule
\end{tabular}
\caption{Socket events between TTC server and clients}
\label{tab:socket-events}
\end{table*}



\subsection{Technology Stack}

This system leverages three core AI models to enable natural voice-based interaction: Automatic Speech Recognition (ASR), Text-to-Speech (TTS), and a Large Language Model (LLM).

\subsubsection{ASR}
\textbf{Whisper} (OpenAI) handles speech-to-text conversion. The system uses the \texttt{openai-whisper} library to transcribe microphone input in real-time. We use the \texttt{small} model (244M parameters). Since Whisper does not natively support streaming, we implemented a custom async pipeline that accumulates audio chunks, transcribes them incrementally, and uses silence detection to emit end-of-utterance events.
\subsubsection{TTS}
\textbf{Chatterbox-Turbo} (ResembleAI) converts agent text back to speech. This model supports audio prompt conditioning, allowing voice cloning from sample recordings. Since Chatterbox-Turbo does not natively support streaming, audio chunks are queued and played sequentially via \texttt{sounddevice} to achieve pseudo-streaming playback.

\subsubsection{LLM}
\textbf{Llama 3.2} (via Ollama) powers the conversational AI. The model is accessed through LangChain's \texttt{ChatOllama} interface with streaming enabled. Responses are yielded incrementally as full sentences are completed. The teacher and student clients each run independent instances of Llama 3.2, enabling separate conversational flows and configurable system prompts for each role.

